---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# mltzostercode

<!-- badges: start -->
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/UBESP-DCTV/mltzostercode?branch=master&svg=true)](https://ci.appveyor.com/project/UBESP-DCTV/mltzostercode)
[![Travis build status](https://travis-ci.org/UBESP-DCTV/mltzostercode.svg?branch=master)](https://travis-ci.org/UBESP-DCTV/mltzostercode)
<!-- badges: end -->

The goal of mltzostercode is to Collect the function and the code used
for the analyses reported in the paper "Use of Machine Learning
techniques for case-detection of Varicella Zoster using routinely
collected textual ambulatory records"

## Installation

To access to all the function provided and their documentation, you can
install the development version of the packagefrom
[GitHub](https://github.com/) with:

```{r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("UBESP-DCTV/mltzostercode")
```

## Analyses

The analyses for the paper are reported in `inst/analysis/analysis.R`.

> NOTE: to be sure you have installed all the needed package used in
        the script `inst/analysis/analysis.R` too, you can install 
        the package with the option `dependencies = TRUE`.

## Code of Conduct
Please note that the 'mltzostercode' project is released with a
[Contributor Code of Conduct](.github/CODE_OF_CONDUCT.md). By
contributing to this project, you agree to abide by its terms.
