---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# mltzostercode

<!-- badges: start -->
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/UBESP-DCTV/mltzostercode?branch=master&svg=true)](https://ci.appveyor.com/project/CorradoLanera/mltzostercode)
[![Travis build status](https://travis-ci.org/UBESP-DCTV/mltzostercode.svg?branch=master)](https://travis-ci.org/UBESP-DCTV/mltzostercode)
<!-- badges: end -->

The goal of mltzostercode is to Collect the function and the code used
for the analyses reported in the paper "Use of Machine Learning
techniques for case-detection of Varicella Zoster using routinely
collected textual ambulatory records"

## Installation

To access to all the function provided and their documentation, you can
install the development version of the packagefrom
[GitHub](https://github.com/) with:

```{r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("UBESP-DCTV/mltzostercode")
```

## Analyses

The analyses for the paper are not a part of the package core. They are
reported in `inst/analysis/analysis.R`. You can find them directly on
github in that folder, or (once the package will be installed) you can
find it under the folder 
`system.file("analysis/analysis.R", package = "mltzostercode")`.

> **NOTE**: The script for the analysis reported in the paper are
included in the package to show the exact procedure followed only. We
cannot provide the data used for the analysis. Hence, at the end of the
day, it cannot run by itself.

> **NOTE 2**: to be sure you have installed all the needed package to
run the script `inst/analysis/analysis.R` (maybe on your data), you may
install the package with the option `dependencies = TRUE`.

> **NOTE 3**: To run the script `inst/analysis/analysis.R`, in its part
involving the _Maximum Entropy_ analyses too, you need the **maxent**
package, which has been removed from the CRAN. Hence, if you want to run
`inst/analysis/analysis.R`, you need to build **maxent** from source by
your own. You can find the archived versions
[here](https://cran.r-project.org/src/contrib/Archive/maxent/).


## Code of Conduct
Please note that the 'mltzostercode' project is released with a
[Contributor Code of Conduct](.github/CODE_OF_CONDUCT.md). By
contributing to this project, you agree to abide by its terms.
